\documentclass[12pt]{article}
\usepackage[usenames]{color} %used for font color
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\usepackage[utf8]{inputenc} %useful to type directly diacritic characters
\usepackage{graphicx}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\graphicspath{ {./} }
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\prob}{\mathbb{P}}

\author{Tianshuang (Ethan) Qiu}
\begin{document}
\title{Homework 3}
\maketitle
\newpage

\section{Ross 8.2}

\subsection{a}
When $n>0$, both the numerator and the denomator is greater than 0, so $a_n > 0 \forall n>0$. Now consider $x_n = \frac{n}{n^2} = \frac{1}{n}$, the denomator is less than $a_n$, so $x_n > a_n \forall n>0$.
\newline
Obviously 0 converges to 0, and we have proven in class that $\frac{1}{n}$ converges to 0 (pick $N = \frac{1}{\epsilon}$). $a_n \to 0$ by squeeze theorem.


\subsection{c}
This sequence converges to $\frac{4}{7}$. We will try to show that $x_n = |c_n-\frac{4}{7}| \to 0$.
\newline
$$|c_n-\frac{4}{7}| = |\frac{28n+21}{49n-35} - \frac{4(7n-5)}{49n-35}|$$
$$= \frac{28n+21-28n+20}{49n-35}$$
$$= \frac{41}{49n-35}$$
$$\lim x_n = 41 \times \lim (\frac{1}{49n-35})$$
Once again, we squeeze this sequence with 0 and $\frac{1}{n}$. Since the denomator is positive $x_n > 0 \forall n>0$, and $49n-35 > n \forall n>\frac{35}{48}$, so $x_n < \frac{1}{n}$ when $n$ is large. Therefore $\frac{1}{49n-35} \to 0$ by squeeze theorem.
\newline
Therefore $\lim x_n = 49 \times 0 = 0$, and $c_n \to \frac{4}{7}$


\subsection{e}
The sequence converges to 0. We define $x_n = \frac{1}{n}, y_n = \frac{-1}{n}$. Since $-1 \leq \sin n \leq 1$, $y_n \leq s_n \leq x_n$.
\newline
We have shown above that $\frac{1}{n} \to 0$. $\frac{-1}{n}$ can be shown with the same reasoning to converge $\forall n>\frac{1}{\epsilon}$. Therefore $s_n \to 0$ by squeeze theorem.
\newpage


\section{Q2}
\subsection{a}
We will prove this via induction.
\newline
Base case: n = 1, $LHS = 1+a; RHS = \frac{1-a^{2}}{1-a}$. $1-a^2 = (1+a)(1-a)$, therefore LHS = RHS. Base case holds.
\newline
Inductive hypothesis, let the claim hold for an arbitrary $n \in \N$.
$$1+a+...+a^n+a^{n+1} = \frac{1-a^{n+1}}{1-a}+a^{n+1}$$
$$=\frac{1-a^{n+1}+a^{n+1}-a^{n+2}}{1-a}$$
$$=\frac{1-a^{n+2}}{1-a}$$
Thus we have proven the inductive hypothesis. Q.E.D.

\subsection{b}
Since $|s_{n+1}-s_n|<1/2^n \forall n$, $|s_{n+2}-s_n| \leq 1/2^n + 1/2^{n+1}$ by the triangle inequality. We can further extend this so $|s_{n+k}-s_n| \leq 1/2^n + 1/2^{n+1} + ... +1/2^{n+k-1}$
\newline
Let $\epsilon > 0$, we pick $N = \max \{ \log_2 (1/\epsilon), 1\}$. Pick $j,k > N$.
$$|s_j - s_k| \leq \sum ^{j+k-1}_{i=j} \frac{1}{2^i} = \frac{1}{2^j}(1+1/2+...+1/2^{k-1})$$
$$=\frac{1}{2^j}(2(1-1/2^{k})) = \frac{1-1/2^k}{2^{j-1}} \leq \frac{1}{2^j}$$
Since $j> \log_2 (1/\epsilon$), $|s_j - s_k|\leq \frac{1}{2^j} < \epsilon$.
\newline
Therefore the sequence is cauchy. Q.E.D.
\newpage


\section{Ross 10.7}
We essentially want to slowly pick items in $S$ that is closer to $\sup S$.
\newline
Consider $x_n = \sup S - 1/n$. Since $x_n < \sup S, \exists s_n \in S s.t. x_n \leq s_n < \sup S$. Both $x_n$ and $\sup S$ converge to $\sup S$, therefore $s_n \to \sup S$ by squeeze theorem.
\newpage


\section{Q4}
Since $s_n \to s$ by our assumption, let $\epsilon > 0, \exists N s.t. \forall n>N, |s_n - s| < \epsilon$.
\newline
Therefore $s-\epsilon < s_n < s + \epsilon$. Since $s_n$ is between these two end points, and since the $\lim \inf$ is non-decreasing, we have $\lim \inf s_n \geq s-\epsilon$.
\newline
Since $\epsilon$ can be arbitrarily small, we must have $\lim \inf s_n \geq s$. Q.E.D.
\newpage


\section{Q5}
\subsection{a}
We will attempt to prove this via induction.
\newline
Base case: $n = 1, s_n = 2, 2^2-2 >0$
\newline
Inductive case: assume that $s_n^2>2$, then $$s_{n+1}^2-2 = \frac{s_n^2}{4} + \frac{1}{s_n^2} + 2$$. Since $s_n^2 > 2, \frac{s_n^2}{4}>0, \frac{1}{s_n^2}>0$. So $s_{n+1}^2 > 2$.
\newline
$s_n^2 -2> 0 \forall n \in \N$

\subsection{b}
We first prove that $s_n > 0 \forall n \in \N$. $n = 1, s_n = 2, 2>0$.
\newline
In the inductive case, assume $s_n > 0$, so $s_n/2 > 0, 1/s_n>0$, therefore $s_n{n+1}>0$. We have proven the inductive case.
\newline
To prove that it is monotone will again use induction.
\newline
Base case: $n = 1, s_n = 2, s_{n+1} = 2/2 + 1/2 = 3/2$, $s_{n+1}<s_n$. The base case holds.
\newline
Inductive case: assume that $s_n < s_{n-1}$. Consider $s_n-s_{n+1} = s_n - \frac{s_n}{2} - \frac{1}{s_n}$
$$\frac{s_n}{2} - \frac{1}{s_n} = \frac{s_n^2-2}{2s_n}$$
We have shown that $s_n^2 -2> 0 $ and that $s_n>0$, so this fraction is positive, therefore $s_n > s_{n+1}$. This sequence is monotonically decreasing.
\newline
Furthermore, since $0<s_n<2$, the sequence is bounded above and below. Therefore it converges. Q.E.D.
\newpage


\section{Q6}
\subsection{a}
$\lim s_n = \sqrt2$.
\newline
We have shown that the sequence converges, so it is also cauchy. Let $\epsilon > 0$, there exists $N$ such that for $ i> N, |s_i - s_{i+1}| < \epsilon$.
\newline
Since $\epsilon$ can get arbitrarily small and that it converges, at very large values of $n$, $s_n$ should be very close the the limit and to $s_{n+1}$. We should have $\lim_{n \to \infty} s_n= \lim_{n \to \infty} s_{n+1}$. Therefore $\lim s_n$ should satisfy $$\lim s_n = \frac{\lim s_n}{2}+ \frac{1}{\lim s_n}$$
$$(\lim s_n)^2 = \frac{\lim s_n^2}{2} + 1$$
$$\frac{1}{2}(\lim s_n)^2 = 1$$
$$(\lim s_n)^2 = 2$$
$$\lim s_n= \sqrt2$$

\subsection{b}
The sequence $s_n$ has $s_n \in \Q$ because each term is the sum of two rationals. Since it is convergent, the sequence is cauchy, but $s_n \to \sqrt 2$, which is an irrational.
\newpage


\section{Q7}
\subsection{a}
Since the sequence is $-1$ when $n$ is odd and $1$ otherwise, it oscillates ad infinitum. $-1 \leq s_n \leq 1$, so $\lim \inf s_n = -1, \lim \sup s_n = 1$
\newline
Let $x_n = \{ s_n | n \bmod 2 \equiv 1\} = \{-1, -1, -1 ...\}$. Since $x_n = -1 \forall n \in \N$, $x_n \to -1 = \lim \inf$
\newline
Let $y_n = \{ s_n | n \bmod 2 \equiv 0\} = \{1, 1, 1 ...\}$. Since $y_n = 1 \forall n \in \N$, $x_n \to 1 = \lim \sup$

\subsection{b}
We claim that $s_n \to 0$.
\newline
Let $\epsilon > 0$, choose $N = \log_2(1/\epsilon)$, $\forall n > N, |s_n-0| = |s_n| = \frac{1}{2^n}$
$$\frac{1}{2^n} < \frac{1}{2^N} = \epsilon$$
Therefore the sequence converges to 0.
\newline
Since we have proven that a sequence converges $iff$ its $\lim \inf = \lim \sup$, we have $\lim \inf s_n= \lim \sup s_n = 0$
\newline
Define $x_n = \{ s_n | n \bmod 2 \equiv 1\}$. Since we are only taking odd $n$'s from the set, $x_n < 0$, and since a subsequence of a convergent sequence also converges to its limit, $x_n \to \lim \inf$
\newline
By the same logic we define Define $y_n = \{ s_n | n \bmod 2 \equiv 0\}$. We can see that $y_n > 0$, and by the convergence theorem stated above we have $y_n \to \lim \sup s_n= 0$

\subsection{c}
Using the limit theorem we can break this down into $\lim (-1)^n$ and $\lim 1/n$. From the work above and in class proofs we have $\lim \inf s_n = -1 + 0 = -1$ and $\lim \sup s_n = 1 + 0 = 1$
\newline
Similar to (a), we define $x_n = \{ s_n | n \bmod 2 \equiv 1\} = (-1)^{2n-1} + 1/(2n-1)$. $\lim x_n = \lim (-1)^{2n-1} + \lim 1/(2n-1)$. The former is constant while the latter is a subsequence of $1/n$ so it converges to 0. Moreover, this sequence only decreasing due to $1/n$ so it is monotone. Finally we have $\lim x_n = \lim \inf s_n = -1$
\newline
Then we define $y_n = \{ s_n | n \bmod 2 \equiv 0\} = (-1)^{2n} + 1/(2n) = 1+1/(2n)$. By the same logic as above the first term converges to 1 while the second converges to 0. It is also monotonically decreasing for the same reason. Finally we have $\lim y_n = \lim \sup s_n = 1$

\end{document}
